---
title: '"worksheet3b"'
author: "Nikkko Bryan Bernardo"
date: "2022-11-23"
output: pdf_document
---

1. Create a data frame using the table below.
a.Write the codes.

```{r, error=TRUE}
Respondents <- c(seq(1,20))
Sex <- c(2,2,1,2,2,2,2,2,2,2,1,2,2,2,2,2,2,2,1,2)
FathersOccupation <- c(1,3,3,3,1,2,3,1,1,1,3,2,1,3,3,1,3,1,2,1)
Personsathome <- c(5,7,3,8,5,9,6,7,8,4,7,5,4,7,8,8,3,11,7,6) 
Siblingsatschool <- c(6,4,4,1,2,1,5,3,1,2,3,2,5,5,2,1,2,5,3,2)
Typesofhouses <- c(1,2,3,1,1,3,3,1,2,3,2,3,2,2,3,3,3,3,3,2)

DataFrame <- data.frame(Respondents,Sex,FathersOccupation,Personsathome,Siblingsatschool,Typesofhouses)
DataFrame
```


b.Describe the data. Get the structure or the summary of the data

```{r, error=TRUE}
summary(DataFrame)
```


c. Is the mean number of siblings attending is 5?
No 

d. Extract the 1st two rows and then all the columns using the subsetting functions.
Write the codes and its output.

```{r, error=TRUE}
C1 <- subset(DataFrame[1:2, 1:6, drop = FALSE])
C1
```
e. Extract 3rd and 5th row with 2nd and 4th column. Write the codes and its result.

```{r, error=TRUE}

C2 <- subset(DataFrame[c(3,5),c(2,4)])
C2
```
f. Select the variable types of houses then store the vector that results as types_houses.
Write the codes.

```{r, error=TRUE}
C3 <- DataFrame[c(6)]

types_houses <- C3
```


g. Select only all Males respondent that their father occupation was farmer. Write
the codes and its output.

```{r, error=TRUE}
C22 <- subset(DataFrame[c(3,11),c(2,3)])
C22
```
h. Select only all females respondent that have greater than or equal to 5 number
of siblings attending school. Write the codes and its outputs

```{r, error=TRUE}
C5 <- subset(DataFrame[c(1:20), c(2,5)])
Fem <- C5[DataFrame$Siblingsatschool >= 5,]
Fem
```
2. Write a R program to create an empty data frame. Using the following codes:

```{r, error=TRUE}
  df = data.frame(Ints=integer(),
            Doubles=double(), Characters=character(),
            Logicals=logical(),
            Factors=factor(),
            stringsAsFactors=FALSE)

print("Structure of the empty dataframe:")
print(str(df))
```
a. Describe the results.
There is no data available in the table.

3. Interpret the graph.



